Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
Added result table draft.
Changes on section 2

>>>>

%------------------------------------
\subsection{Sampling and Holding in Hybrid Systems}
\label{ssec:SandH}
%------------------------------------

The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants. Thus, the proposed approach have to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller have to consider the issues related to the hybrid systems studies.

For this purpose, the design procedure is based on a discretized model for a continuous plant. For transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.
